---
title: "R Notebook"
output:
  html_document:
    df_print: paged
    toc: true
    toc_depth: 3

---

# Groundhog

This is concerned with sustaining reproducible scripts.

```{r}
install.packages('groundhog') # install groundhog
library(groundhog) # load groundhog
pkgs <- c("tidyverse", "here") # what packages do you want
groundhog.day <- '2022-08-25' # and at what point in time do you want those packages
groundhog.library(pkgs, groundhog.day) # install and load those packages as they existed on that date
```

# Pacman

Pacman allows you to load multiple packages at once

```{r}
install.packages("pacman")
pacman::p_load(tidyverse, here)
```

If you use Pacman, you don't need to use Groundhog and vica versa. 

# Here

```{r}
here::i_am("Level 1/Level 2/Level 3/test.Rmd")
data("mtcars")
write.csv(mtcars, here::here("Level 1", "Level 2", "Level 3", "mtcars.csv"))
```

# Report

```{r}
m <- lm(mpg ~ qsec, data = mtcars)
summary(m)

install.packages('report')
library(report)

report(m)
```

# Performance

1. Linear relationship: There exists a linear relationship between the independent variable, x, and the dependent variable, y.

2. Independence: The residuals are independent. In particular, there is no correlation between consecutive residuals in time series data.

3. Homoscedasticity: The residuals have constant variance at every level of x.

4. Normality: The residuals of the model are normally distributed.

## Use check_model()

```{r}
library(performance)
check_model(m)
```


## Use check_zeroinflation(model) and check_overdispersion() from library(glmmTMB) data(Salamanders)

```{r}
install.packages("glmmTMB")
library(glmmTMB)
data(Salamanders)
model <- glm(count ~ spp + mined, family = poisson, data = Salamanders)

check_overdispersion(model)

check_zeroinflation(model)
```

```{r}
model <- MASS::glm.nb(count ~ spp + mined, data = Salamanders)

check_overdispersion(model)

check_zeroinflation(model)
```




